Galois Slicing as Differentiation

### 2025-07-11 main/approx-as-tangents.tex
the

\begin{proof}
  If $f$ is stable, then define a left adjoint
  $f^*_x : \downset{f(x)} \to \downset{x}$ by setting $f^*_x(y)$ to be
  the minimal $x_0$ required by stability. This is monotone: if
  $y \leq y'$, then we know that $y \leq y' \leq f(f^*_x(y'))$ by
  definition of $f^*_x$, so $f^*_x(y) \leq f^*_x(y')$ by minimality of
  $f^*_x(y)$. For the adjointness, let $x' \leq x$ and $y \leq
  f(x)$. Then if $f^*_x(y) \leq x'$, we have
  $y \leq f(f^*_x(y)) \leq f(x')$ by monotonicity of $f$ and the first
  part of stability. In the other direction, if we have
  $y \leq f(x')$, then by uniqueness we have $f^*_x(y) \leq x'$.

>>>>

\begin{proof}
  If $f$ is stable, then define a left adjoint
  $f^*_x : \downset{f(x)} \to \downset{x}$ by setting $f^*_x(y)$ to be
  the minimal $x_0$ required by stability. This is monotone: if
  $y \leq y'$, then we know that $y \leq y' \leq f(f^*_x(y'))$ by the
  definition of $f^*_x$, so $f^*_x(y) \leq f^*_x(y')$ by minimality of
  $f^*_x(y)$. For the adjointness, let $x' \leq x$ and $y \leq
  f(x)$. Then if $f^*_x(y) \leq x'$, we have
  $y \leq f(f^*_x(y)) \leq f(x')$ by monotonicity of $f$ and the first
  part of stability. In the other direction, if we have
  $y \leq f(x')$, then by uniqueness we have $f^*_x(y) \leq x'$.
